---
title: "Zürich (CH) Airport"
subtitle: "Prediction of delays"
author: "Alexis Barrière"
date: "13/02/2020"
output: pdf_document
toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if(!require(tidyverse)) install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require(caret)) install.packages("caret", repos = "http://cran.us.r-project.org")
if(!require(data.table)) install.packages("data.table", repos = "http://cran.us.r-project.org")
if(!require(gridExtra)) install.packages("gridExtra", repos = "http://cran.us.r-project.org")
if(!require(ggthemes)) install.packages("ggthemes", repos = "http://cran.us.r-project.org")
if(!require(randomForest)) install.packages("randomForest", repos = "http://cran.us.r-project.org")

comma <- function(x){
  format(x,digits = 2,big.mark = "\\'")
}
```

\newpage

# Introduction

This project will use data of planned and effective flight arrival and departure-times from / to the airport of Zurich in Switzerland for the entire year 2017.  
These data have been collected for the TWIST 2018 Hackdays in Zürich (https://www.twist2018.ch/).  
Some work has already been done by the team to enhance and clean the data:

* add information concerning the origin or destination airport as the geographical data and the distance  (source : http://ourairports.com/data/)
* add weather information concerning Zürich airport (temperature, precipitation, lightning, humidity, ...) (source : MeteoSchweiz, free only for universities)
* compute delays from effective minus planned time

The goal of this project is to find the best prediction of delays and find the best predictors of the delay (company, airplane type, weather, distance, ...)


# Data Analysis


## Data Loading

The data can be retrieve from Github:
```{r RDSdata, eval=FALSE}
url <- "https://github.com/tlorusso/twist_zrh/raw/master/twist_zrh.RDS"
temp <- tempfile() # create a tempfile
download.file(url, temp) # download to disk
dat <- readRDS(temp) # read the tempfile
unlink(temp) # Deletes tempfile
```

but for some reason the readRDS function is failing with this direct download. I have then dowloaded the file on my repository and then I have been able to read the file:
```{r dataload, cache = TRUE}
twist_zrh_clean <- readRDS("./data/twist_zrh_cleaned.RDS")
```

We can then see that our dataset have `r comma(nrow(twist_zrh_clean))` observables and `r comma(ncol(twist_zrh_clean))` variables.

The first step is to clean some of our variables, because they are factors but have not been "refactored" after the first cleaning.
We will also create some more variables to  make our analysis (month, hour and flight type).
And then delete some uninteresting variables
```{r datacleaning, cache=TRUE}
flightdata <- twist_zrh_clean %>%
  mutate(continent=as.character(continent),
         airline_name=as.character(airline_name),
         airplane_type=as.character(airplane_type),
         origin_destination_name=as.character(origin_destination_name),
         airport_type=as.character(airport_type),
         iso_country=as.character(iso_country),
         iso_region=as.character(iso_region),
         municipality=as.character(municipality),
         month = month(date),
         hour = hour(planed_time),
         flight_type=ifelse(start_landing=="L","Landing","Take-Off"))
flightdata <- flightdata %>%
  mutate(continent=replace_na(continent,"NA"))
flightdata <- flightdata %>%
  mutate(continent=as.factor(continent),
         airline_name=as.factor(airline_name),
         airplane_type=as.factor(airplane_type),
         airport_type=as.factor(airport_type),
         iso_country=as.factor(iso_country),
         iso_region=as.factor(iso_region),
         month = as.factor(month),
         hour = as.factor(hour),
         flight_type=as.factor(flight_type)) %>%
  rename(c("delay_sec"="diff_in_secs"))
flightdata <- flightdata %>%
  select(-tde200h0) %>% select(-start_landing)
```

Unfortunately the weather data are finishing on the $30^{th}$ of December, so in order to have a cleaned dataset with all relevant variables, we will delete data of the $31^{st}$ of December.
```{r badweatherdelete, cache=TRUE}
flightdata <- flightdata %>% filter(!is.na(temp_avg))
```


## Data Exploration


Now we can have a look at the variable we want to predict, the delay:

```{r delaysummary, echo=FALSE, cache=TRUE}
Landing <- flightdata %>% filter(flight_type=="Landing")
knitr::kable(data.frame(Min=as.numeric(summary(as.numeric(Landing$delay_sec))[1]),
           'First Qu.'=as.numeric(summary(as.numeric(Landing$delay_sec))[2]),
           Median=as.numeric(summary(as.numeric(Landing$delay_sec))[3]),
           Mean=as.numeric(summary(as.numeric(Landing$delay_sec))[4]),
           'Third Qu.'=as.numeric(summary(as.numeric(Landing$delay_sec))[5]),
           Max=as.numeric(summary(as.numeric(Landing$delay_sec))[6])),caption="Landing Delay summary statistics")
TakeOff <- flightdata %>% filter(flight_type=="Take-Off")
knitr::kable(data.frame(Min=as.numeric(summary(as.numeric(TakeOff$delay_sec))[1]),
           'First Qu.'=as.numeric(summary(as.numeric(TakeOff$delay_sec))[2]),
           Median=as.numeric(summary(as.numeric(TakeOff$delay_sec))[3]),
           Mean=as.numeric(summary(as.numeric(TakeOff$delay_sec))[4]),
           'Third Qu.'=as.numeric(summary(as.numeric(TakeOff$delay_sec))[5]),
           Max=as.numeric(summary(as.numeric(TakeOff$delay_sec))[6])),caption="Take-Off Delay summary statistics")
```

We will split the data by Flight Type as it's really two different thing.

To have more relevant data, we will only take airlines with at least 500 flights (arrival or departure) during the year:

```{r airlineselect, message=FALSE,cache=TRUE}
airline <- flightdata %>%
  group_by(airline_name) %>%
  summarize(NbFlights=n()) %>%
  filter(NbFlights>500) %>%
  select(airline_name)

flightdata <- inner_join(flightdata,airline,by="airline_name")

flightdata$airline_name <- factor(flightdata$airline_name)
flightdata$airplane_type <- factor(flightdata$airplane_type)
```

We can also add another categorization variable based on the delay which tell if a flight is early (delay in seconds < 0), if there is no delay (delay between 0 seconds and 15 minutes) or if there is a delay (more than 15 minutes of delay):

```{r delay_category_create}
flightdata <- flightdata %>%
  mutate(delay_cat = cut(as.numeric(delay_sec),
                         breaks = c(-Inf,0,900,Inf),
                         labels = c("Early","No Delay","Delay")))
```

Which gives us this split :

```{r delay_category, echo=FALSE, warning=FALSE}
knitr::kable(flightdata %>%  
               group_by("Flight Type"=flight_type,"Delay Category"=delay_cat) %>%  
               summarise("Nb of Flights"=comma(n())),caption = "Number of Flights by Delay Category")
```

In the table 1 and 2, we see that we have extreme values that seems way off our inner quartile. Let's see it with a boxplot:

```{r delayboxplot, echo=FALSE, warning=FALSE}
flightdata %>%
  ggplot(aes(x=flight_type ,y=as.numeric(delay_sec))) +
  geom_boxplot() +
  ylab("Delay (sec)") +
  xlab("") + 
#  geom_tile("Delays by Flight Type (Full Dataset)") +
  theme_economist()
```

We can see that the values above 50'000 seconds and below -50'000 seconds are not representative (outliers) and should be deleted to have more relevant data:
```{r deleteextreme}
flightdata <- flightdata %>% filter(abs(delay_sec)<50000)
```

Now let's just have a look closer at the values more around 0 (no delay) :

```{r delayfilterboxplot, echo=FALSE, warning=FALSE, cache = TRUE}
flightdata %>%
  ggplot(aes(x=flight_type ,y=as.numeric(delay_sec))) +
  geom_boxplot() +
  ylim(-7200,7200) +
  ylab("Delay (sec)") + 
#  geom_tile("Delays < 2 hours by Flight Type") +
  theme_economist()
```

So it seems we have different patterns in our two types of flight. Let's see it whith histograms:

```{r delayfilterhistoplot, echo=FALSE, warning=FALSE, message=FALSE, cache = TRUE}
flightdata %>%
  filter(abs(delay_sec) < 7200) %>%
  ggplot(aes(x = delay_sec)) + 
  geom_histogram(bins = 60, col = 1) +
  labs(title = "Asolute delay < 2 hours") +
  ylab("Number of flights") + xlab("Delay (sec)") +
  facet_wrap(~ flight_type) +
  theme_economist()
```

So, what we see is:

* For Landing flight type, the data seem to be more symetric aroung 0 (as much delayed than early flights)
* For Take-Off type, the data are skewed to the right (more delayed flights than early flights)

So in our analysis, we will process this two datasets separately.

We can then have a view on the spread of the delay by airlines:

```{r airlinedelay, echo=FALSE, warning=FALSE, fig.height=10, cache = TRUE}
# Analyze by Airline
flightdata %>% ggplot(aes(x=as.numeric(delay_sec),y=reorder(airline_name,-as.numeric(delay_sec)),col=airline_name)) +
  geom_vline(xintercept = 900) +
  geom_point() + 
  geom_jitter(alpha = 0.5, size = 0.3) + guides( color = FALSE) + ylab(NULL) +
  xlab("Delay (sec)")
```

We can also have a look at the delays based on month of the year:

```{r monthdelay, echo=FALSE, warning=FALSE, message=FALSE, cache = TRUE}
flightdata %>%
  filter(abs(delay_sec) < 7200) %>%
  ggplot(aes(x = month, y = as.numeric(delay_sec))) + 
  geom_boxplot(outlier.size=0) +
  ylab("Delay (sec)") +
  facet_wrap(~ flight_type) +
  theme_economist()
```

This is clearly a seasonal effect due to the fact that there is more flights during End of Year season and Summer Holiday season:

```{r monthdetail, echo=FALSE, warning=FALSE, message=FALSE, cache = TRUE}
knitr::kable(flightdata %>%
  filter(abs(delay_sec) < 7200) %>%
  group_by(month) %>%
  summarize("Nb Flights"=comma(n()),"Mean delay"=comma(mean(as.numeric(delay_sec)))),caption = "Flights by Month detail")
```


The data can also be explored by hour of the day:

```{r hourdelay, echo=FALSE, warning=FALSE, message=FALSE, cache = TRUE}
flightdata %>%
  filter(abs(delay_sec) < 7200) %>%
  ggplot(aes(x = hour, y = as.numeric(delay_sec))) + 
  geom_boxplot(outlier.size=0) +
  ylab("Delay (sec)") +
  facet_wrap(~ flight_type) +
  theme_economist()
```

At least we could have expected a delay increasing as the day went on especially for Take-Off data, but the mean delay is more or less constant. The only thing we notice is that the interquartile is larger at the end of the day that at the beginning, meaning less more variability in the delays.

The last analysis that can help to understand our data is a geographical analysis of the origin or destination of the flights:

```{r continentdelay, echo=FALSE, warning=FALSE, message=FALSE, cache = TRUE}
flightdata %>%
  filter(abs(delay_sec) < 7200) %>%
  ggplot(aes(x = continent, y = as.numeric(delay_sec))) +
  geom_boxplot()+
  ylab("Delay (sec)") +
  facet_wrap(~ flight_type) +
  theme_economist()
```

For the landing part, we clearly see that the gulf stream allows to have a majority of flights to be early. Unlike of the Take-Off flights for America that tends to be always late.


# Prediction, Analysis & Results

The first step will be to split our dataset by Flight Type, Landing or Take Off.
We will also select only a subset of variables to lighten the analysis by keeping only (Airline, Airplane Type, Distance, Windspeed average, Precipitation, temperature average, Air Pressure, Month and Hour)
Finally, we will modify the value we want to predict to make it discrete. The goal will be to predict if a flight is delayed by more than 15 minutes or not.  

```{r datapred}
# Create two datasets for Landing and Take-Off and select meaningfull variable
Landing <- flightdata %>% filter(flight_type=="Landing") %>%
  mutate(delay = as.numeric(delay_sec), delayYN=as.factor((delay>900))) %>%
  select(delayYN,airline_name, airplane_type,distance_km,windspeed_avg_h,
         precip,temp_avg,airpres,hour,month) 
TakeOff <- flightdata %>% filter(flight_type=="Take-Off") %>%
  mutate(delay = as.numeric(delay_sec), delayYN=as.factor((delay>900))) %>%
  select(delayYN,airline_name, airplane_type,distance_km,windspeed_avg_h,
         precip,temp_avg,airpres,hour,month) 
```

First we will split the Take-Off dataset in a training and a test dataset. The test dataset will have around 30% of the data, making sure all airlines, airplane type, month and hour that are in it are also in the training dataset.

```{r TakeOffSplitSet,warning=FALSE,message=FALSE}
set.seed(2020)
TakeOff_index <- createDataPartition(TakeOff$delay, times = 1, p = 0.3, list = FALSE)
TakeOff_test_set <- TakeOff[TakeOff_index, ]
TakeOff_train_set <- TakeOff[-TakeOff_index, ]

temp <- TakeOff[TakeOff_index, ]
# Make sure Ariline in test set are also in training set
TakeOff_test_set <- temp %>% 
  semi_join(TakeOff_train_set, by = "airline_name") %>%
  semi_join(TakeOff_train_set, by = "airplane_type") %>%
  semi_join(TakeOff_train_set, by = "month") %>%
  semi_join(TakeOff_train_set, by = "hour")


# Add rows removed from test set back into training set
removed <- anti_join(temp, TakeOff_train_set)
TakeOff_train_set <- rbind(TakeOff_train_set, removed)

rm(TakeOff_index, temp, removed)
```


We will first try to do a prediction using the logistic regression model using the airline as predictor and then predict with our test set :
```{r glm_TO_A,message=FALSE, warning=FALSE,cache=TRUE}
glm_TO_A <- train(delayYN ~ airline_name, 
                  method = "glm", data = TakeOff_train_set)

delay_hat_glm_TO_A <- predict(glm_TO_A, TakeOff_test_set)
```

This gives us the following metrics:
```{r glm_TO_A_result,echo=FALSE,message=FALSE, warning=FALSE,cache=TRUE}
results_TO <- data_frame(Method = "GLM",
                      Predictors = "Airline",
                      Accuracy = confusionMatrix(delay_hat_glm_TO_A,TakeOff_test_set$delayYN)$overall["Accuracy"],
                      Sensitivity = confusionMatrix(delay_hat_glm_TO_A,TakeOff_test_set$delayYN)$byClass["Sensitivity"],
                      Specifictiy = confusionMatrix(delay_hat_glm_TO_A,TakeOff_test_set$delayYN)$byClass["Specificity"])

results_TO %>% knitr::kable(digits = 4)
```

We can see that even if the Accuracy is quite correct and the Sensitivity really good, we have a very bad Specificity which means the algorithm is really bad at predicting a delay when there is one.
Let's try by adding two more predictors that seems to have importance in our exploratory work, Distance and Hour:
```{r glm_TO_AHD,message=FALSE, warning=FALSE,cache=TRUE}
glm_TO_AHD <- train(delayYN ~ airline_name+hour+distance_km, 
                    method = "glm", data = TakeOff_train_set)

delay_hat_glm_TO_AHD <- predict(glm_TO_AHD, TakeOff_test_set)
```

Which gives us:
```{r glm_TO_AHD_result,echo=FALSE,message=FALSE, warning=FALSE,cache=TRUE}
results_TO <- bind_rows(results_TO,
                          data_frame(Method = "GLM",
                                     Predictors = "Airline+Hour+Distance",
                                     Accuracy = confusionMatrix(delay_hat_glm_TO_A,TakeOff_test_set$delayYN)$overall["Accuracy"],
                                     Sensitivity = confusionMatrix(delay_hat_glm_TO_A,TakeOff_test_set$delayYN)$byClass["Sensitivity"],
                                     Specifictiy = confusionMatrix(delay_hat_glm_TO_A,TakeOff_test_set$delayYN)$byClass["Specificity"]))

results_TO %>% knitr::kable(digits = 4)
```

The results are a bit better. Now we can try with all our predictors:
```{r glm_TO_Full,message=FALSE, warning=FALSE,cache=TRUE}
glm_TO_Full <- train(delayYN ~ airline_name+airplane_type+distance_km+
                       windspeed_avg_h+precip+temp_avg+airpres+hour+month,
                     method = "glm", data = TakeOff_train_set)

delay_hat_glm_TO_Full <- predict(glm_TO_Full, TakeOff_test_set)
```

We can see in the following table that the results are better, especially concerning Specificity, even if it's still not good :
```{r glm_TO_Full_result,echo=FALSE,message=FALSE, warning=FALSE,cache=TRUE}
results_TO <- bind_rows(results_TO,
                     data_frame(Method = "GLM",
                                Predictors = "All",
                                Accuracy = confusionMatrix(delay_hat_glm_TO_Full,TakeOff_test_set$delayYN)$overall["Accuracy"],
                                Sensitivity = confusionMatrix(delay_hat_glm_TO_Full,TakeOff_test_set$delayYN)$byClass["Sensitivity"],
                                Specifictiy = confusionMatrix(delay_hat_glm_TO_Full,TakeOff_test_set$delayYN)$byClass["Specificity"]))

results_TO %>% knitr::kable(digits = 4)
```


We will then try another algorithm to see if we can have better results. So let's try thhe Random Forest algorithm with the 3 same steps :

```{r randfor,message=FALSE, warning=FALSE, cache = TRUE}
randfor_TO_A <- randomForest(delayYN ~ airline_name, 
                             data = TakeOff_train_set)
delay_hat_randfor_TO_A <- predict(randfor_TO_A, TakeOff_test_set)

randfor_TO_AHD <- randomForest(delayYN ~ airline_name+hour+distance_km,
                               data = TakeOff_train_set)
delay_hat_randfor_TO_AHD <- predict(randfor_TO_AHD, TakeOff_test_set)

randfor_TO_Full <- randomForest(delayYN ~ airline_name+airplane_type+distance_km+
                                  windspeed_avg_h+precip+temp_avg+airpres+hour+month,
                                data = TakeOff_train_set)
delay_hat_randfor_TO_Full <- predict(randfor_TO_Full, TakeOff_test_set)
```

This gives us the following results:
```{r randfor_results,echo=FALSE,message=FALSE, warning=FALSE,cache=TRUE}
results_TO <- bind_rows(results_TO,
                     data_frame(Method = "Random Forest",
                                Predictors = "Airline",
                                Accuracy = confusionMatrix(delay_hat_randfor_TO_A, TakeOff_test_set$delayYN)$overall["Accuracy"],
                                Sensitivity = confusionMatrix(delay_hat_randfor_TO_A, TakeOff_test_set$delayYN)$byClass["Sensitivity"],
                                Specifictiy = confusionMatrix(delay_hat_randfor_TO_A, TakeOff_test_set$delayYN)$byClass["Specificity"]))
results_TO <- bind_rows(results_TO,
                     data_frame(Method = "Random Forest",
                                Predictors = "Airline+Hour+Distance",
                                Accuracy = confusionMatrix(delay_hat_randfor_TO_AHD, TakeOff_test_set$delayYN)$overall["Accuracy"],
                                Sensitivity = confusionMatrix(delay_hat_randfor_TO_AHD, TakeOff_test_set$delayYN)$byClass["Sensitivity"],
                                Specifictiy = confusionMatrix(delay_hat_randfor_TO_AHD, TakeOff_test_set$delayYN)$byClass["Specificity"]))
results_TO <- bind_rows(results_TO,
                     data_frame(Method = "Random Forest",
                                Predictors = "All",
                                Accuracy = confusionMatrix(delay_hat_randfor_TO_Full, TakeOff_test_set$delayYN)$overall["Accuracy"],
                                Sensitivity = confusionMatrix(delay_hat_randfor_TO_Full, TakeOff_test_set$delayYN)$byClass["Sensitivity"],
                                Specifictiy = confusionMatrix(delay_hat_randfor_TO_Full, TakeOff_test_set$delayYN)$byClass["Specificity"]))

results_TO %>% knitr::kable(digits = 4, caption = "Take-Off Results")
```

So the first two steps give us approximately the same results as the other algorithm, but if we use all our predictors with the Random Forest, the results are really interesting.
Let's look at the entire confusion matrix of this last prediction to see the details:

```{r confmat, echo=FALSE,message=FALSE, warning=FALSE,cache=TRUE}
confusionMatrix(delay_hat_randfor_TO_Full, TakeOff_test_set$delayYN)$table %>% knitr::kable(caption="Prediction Results")

confusionMatrix(delay_hat_randfor_TO_Full, TakeOff_test_set$delayYN)$byClass %>% knitr::kable(caption = "Model statistics")
```

The first table confirms that we have still some miss predictions but really low compared to the good ones.


We can also do the same work for the Landing dataset:

```{r LandingSet,warning=FALSE,message=FALSE,cache=TRUE}
set.seed(2020)
Landing_index <- createDataPartition(Landing$delayYN, times = 1, p = 0.3, list = FALSE)
Landing_train_set <- Landing[-Landing_index, ]

temp <- Landing[Landing_index, ]
# Make sure Ariline in test set are also in training set
Landing_test_set <- temp %>%
  semi_join(Landing_train_set, by = "airline_name") %>%
  semi_join(Landing_train_set, by = "airplane_type") %>%
  semi_join(Landing_train_set, by = "month") %>%
  semi_join(Landing_train_set, by = "hour")

# Add rows removed from test set back into training set
removed <- anti_join(temp, Landing_train_set)
Landing_train_set <- rbind(Landing_train_set, removed)

rm(Landing_index, temp, removed)


glm_LA_A <- train(delayYN ~ airline_name, method = "glm", data = Landing_train_set)
delay_hat_glm_LA_A <- predict(glm_LA_A, Landing_test_set)

glm_LA_AHD <- train(delayYN ~ airline_name+hour+distance_km, method = "glm", data = Landing_train_set)
delay_hat_glm_LA_AHD <- predict(glm_LA_AHD, Landing_test_set)

glm_LA_Full <- train(delayYN ~ airline_name+airplane_type+distance_km+windspeed_avg_h+precip+temp_avg+airpres+hour+month, method = "glm", data = Landing_train_set)
delay_hat_glm_LA_Full <- predict(glm_LA_Full, Landing_test_set)


randfor_LA_A <- randomForest(delayYN ~ airline_name, data = Landing_train_set)
delay_hat_randfor_LA_A <- predict(randfor_LA_A, Landing_test_set)

randfor_LA_AHD <- randomForest(delayYN ~ airline_name+hour+distance_km, data = Landing_train_set)
delay_hat_randfor_LA_AHD <- predict(randfor_LA_AHD, Landing_test_set)

randfor_LA_Full <- randomForest(delayYN ~ airline_name+airplane_type+distance_km+windspeed_avg_h+precip+temp_avg+airpres+hour+month, data = Landing_train_set)
delay_hat_randfor_LA_Full <- predict(randfor_LA_Full, Landing_test_set)
```

This gives us the following results for Landing

```{r LandingResult, echo=FALSE,message=FALSE, warning=FALSE,cache=TRUE}
results_LA <- data_frame(Method = "GLM",
                         Predictors = "Airline",
                         Accuracy = confusionMatrix(delay_hat_glm_LA_A,Landing_test_set$delayYN)$overall["Accuracy"],
                         Sensitivity = confusionMatrix(delay_hat_glm_LA_A,Landing_test_set$delayYN)$byClass["Sensitivity"],
                         Specifictiy = confusionMatrix(delay_hat_glm_LA_A,Landing_test_set$delayYN)$byClass["Specificity"])

results_LA <- bind_rows(results_LA,
                        data_frame(Method = "GLM",
                                   Predictors = "Airline+Hour+Distance",
                                   Accuracy = confusionMatrix(delay_hat_glm_LA_AHD,Landing_test_set$delayYN)$overall["Accuracy"],
                                   Sensitivity = confusionMatrix(delay_hat_glm_LA_AHD,Landing_test_set$delayYN)$byClass["Sensitivity"],
                                   Specifictiy = confusionMatrix(delay_hat_glm_LA_AHD,Landing_test_set$delayYN)$byClass["Specificity"]))

results_LA <- bind_rows(results_LA,
                        data_frame(Method = "GLM",
                                   Predictors = "All",
                                   Accuracy = confusionMatrix(delay_hat_glm_LA_Full,Landing_test_set$delayYN)$overall["Accuracy"],
                                   Sensitivity = confusionMatrix(delay_hat_glm_LA_Full,Landing_test_set$delayYN)$byClass["Sensitivity"],
                                   Specifictiy = confusionMatrix(delay_hat_glm_LA_Full,Landing_test_set$delayYN)$byClass["Specificity"]))

results_LA <- bind_rows(results_LA,
                        data_frame(Method = "Random Forest",
                                   Predictors = "Airline",
                                   Accuracy = confusionMatrix(delay_hat_randfor_LA_A, Landing_test_set$delayYN)$overall["Accuracy"],
                                   Sensitivity = confusionMatrix(delay_hat_randfor_LA_A, Landing_test_set$delayYN)$byClass["Sensitivity"],
                                   Specifictiy = confusionMatrix(delay_hat_randfor_LA_A, Landing_test_set$delayYN)$byClass["Specificity"]))

results_LA <- bind_rows(results_LA,
                        data_frame(Method = "Random Forest",
                                   Predictors = "Airline+Hour+Distance",
                                   Accuracy = confusionMatrix(delay_hat_randfor_LA_AHD, Landing_test_set$delayYN)$overall["Accuracy"],
                                   Sensitivity = confusionMatrix(delay_hat_randfor_LA_AHD, Landing_test_set$delayYN)$byClass["Sensitivity"],
                                   Specifictiy = confusionMatrix(delay_hat_randfor_LA_AHD, Landing_test_set$delayYN)$byClass["Specificity"]))

results_LA <- bind_rows(results_LA,
                        data_frame(Method = "Random Forest",
                                   Predictors = "All",
                                   Accuracy = confusionMatrix(delay_hat_randfor_LA_Full, Landing_test_set$delayYN)$overall["Accuracy"],
                                   Sensitivity = confusionMatrix(delay_hat_randfor_LA_Full, Landing_test_set$delayYN)$byClass["Sensitivity"],
                                   Specifictiy = confusionMatrix(delay_hat_randfor_LA_Full, Landing_test_set$delayYN)$byClass["Specificity"]))

results_LA %>% knitr::kable(digits = 4,caption = "Landing Results")
```

We can see that we obtain the same type of result for Landing, confirming that the Random Forest Model is a good model for our analysis.


# Conclusion

The results obtained with the Random Forest algorithm and considering all the predictors are really interesting and is a really good start to find a good algorithm to know if our flight will be delayed or not.

To improve our results, we could consider:

* tune our Random Forest algorithm with cross-validation to find the best parameters
* add weather condition of origin (for Landing flights) or destination (for Take-Off flights) airport.
* add information of number of passengers or fill percentage of airplane
